---
title: "ballot"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
dir <- "~/Dropbox/EL155s"
library(tidyverse)
library(foreach)
library(ballot)
library(purrr)
library(fs)
library(data.table)
```


Install by 

```{r, eval = FALSE}
devtools::install_github("kuriwaki/ballot")
```



# Wrapper

A wrapper across all counties in a given election is 

```{r}
subdirs <- dir_ls(path(dir, "input/SC_2017-11-28"), recursive = FALSE)
df <- suppressWarnings(read_format_EL155(subdirs))
```

To do this county by county, see the following.


# Each Function Separately

## `read_EL155`

Read the EL155 file (raw file output for ballot images) and format. 

```{r}
p2016 <- read_EL155(path(dir, "input/SC_2016-06-14/Spartanburg/EL155"), "Spartanburg")
p2016
```

## `get_precinct`

Add precinct identifier to each row

```{r}
pkey <- get_precinct(p2016)
head(pkey)
p2016_precinct <- add_precinct(p2016, pkey)
p2016_precinct
```

## `parse_EL155`

Parse the text with pre-specified fixed width. 
```{r}
p2016_parsed <- parse_EL155(p2016_precinct)
p2016_parsed
```


## `identify_voter`

Add a unique ID for each voter
```{r}
with_voter <- identify_voter(p2016_parsed)
```


## `add_id`

Add voter identifier that will be unique with many counties

```{r}
df <- add_id(with_voter)
```

